DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-18 paper/intro.tex
Add GitHub link

% contributions
The {\bf contributions} of this paper are as follows:
\begin{itemize}
  \item We present DeepPicar, a low-cost autonomous car testbed using
    a state-of-the-art CNN for end-to-end real-time control, to lower
    economic and safety-related barriers to the study autonomous
    cars.~\footnote{The source code, dataset, and build instructions
      of DeepPicar can be found at:\fixme{Michael github url}}

>>>>

% contributions
The {\bf contributions} of this paper are as follows:
\begin{itemize}
  \item We present DeepPicar, a low-cost autonomous car testbed using
    a state-of-the-art CNN for end-to-end real-time control, to lower
    economic and safety-related barriers to the study autonomous
    cars.~\footnote{The source code, dataset, and build instructions
      of DeepPicar can be found at: \url{https://github.com/mbechtel2/DeepPicar-v2}}
